%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage[T1]{fontenc}
\usepackage{anyfontsize}
\usepackage{xcolor}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Aovi Deshpande}
\def \subtitle {4th year Undergraduate in Chemical Engineering}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/aovi-deshpande-9b29a8185}
\def \linkedintext {/aovi-deshpande}

\def \phoneicon {\faPhone}
\def \phonetext {+91 8830167207}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:aovideshpande@gmail.com}
\def \emailtext {aovideshpande@gmail.com}

% \def \githubicon {\faGithub}
% \def \githublink {https://github.com/dwight-schrute}
% \def \githubtext {/dwight-schrute}

% \def \websiteicon {\faGlobe}
% \def \websitelink {https://google.com/}
% \def \websitetext {dwightschrute.com}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{002334}
\definecolor{secondary}{HTML}{0D47A1}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{1565C0}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabular*}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabular*}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    {
      \begin{tabular}[c]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabular*}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabular*}
}

\begin{document}

\headertype{\linkedin}{}{}{\phone}{\email}{} % Set the order of items here
\vspace{3pt} % Set a negative value to push the body up, and the opposite

\section{\faGraduationCap}{Education}

\resumeEntryStart
  \resumeEntryTSDL
      {Shivajirao S. Jondhale College of Engineering}{2017 -- 2021}
      {B.Tech, Department of Chemical Engineering}{Mumbai, India}
     \item[]\small{\color{primary}CGPA -- { \textbf{9.01/10} \vspace{-6pt}}}
  \resumeEntryEnd
  \vspace{3pt}


\resumeEntryStart
  \resumeEntryTSDL
      {Pandit Bachraj Vyas Vidyalaya}{2015 -- 2017}
      {Higher Secondary, Maharashtra State Board}{Nagpur, India}
     \item[]\small{\color{primary}Score -- { \textbf{76/100} \vspace{-6pt}}}
  \resumeEntryEnd
  \vspace{3pt}


\resumeEntryStart
  \resumeEntryTSDL
      {Chanda Devi Saraf High School}{2004 -- 2015}
      {Secondary School, Indian Certificate of Secondary Education}{Nagpur, India}
     \item[]\small{\color{primary}Score -- { \textbf{92/100} \vspace{-6pt}}}
  \resumeEntryEnd
  \vspace{3pt}


  \vspace{4pt}
  
\section{\faTrophy}{Internship}

  \resumeEntryStart
      \resumeEntryTD
      {Adya Group}{Summer 2020}
    \resumeItemListStart
      \resumeItem{Process Simulation  Intern}
      \resumeItem{learned comprehensively about DWSIM and performed simulation on unit operations and process}
      \resumeItem{Generated a report on software uses and  limitations along with one practical project.}
    \resumeItemListEnd
  \resumeEntryEnd


  \resumeEntryStart
      \resumeEntryTD
      {Rashtriya Chemical Factory}{Winter 2019}
    \resumeItemListStart
      \resumeItem{vocational trainee at ammonia plant}
      \resumeItem{overview of urea, argon, heavy water, carbonmonoxide, steam generation plants}
      \resumeItem{vocational trainee at ammonia plant}
    \resumeItemListEnd
  \resumeEntryEnd


  \resumeEntryStart
      \resumeEntryTD
      {Vijay Gas Industries}{Winter 2019}
    \resumeItemListStart
      \resumeItem{Worked as an intern in Ammonia and Nitric Acid manufacturing plant}
      \resumeItem{Performed detailed analysis on various unit operations and their practical applications}
      \resumeItem{Generated a comprehensive report on the working of the plan.}
    \resumeItemListEnd
  \resumeEntryEnd
  

\section{\faTrophy}{Projects}

\resumeEntryStart
      \resumeEntryTD
      {Process Simulation}{Summer 2020}
    \resumeItemListStart
      \resumeItem {Created a start to end process simulation of a three component azeotrope system}
      \resumeItem {The process had nitric acid, HCl and water system which was seperated by a dual pressure swing distillation column}
      \resumeItem {Cost analysis along with debottelnecking and process optimization for the system was also carried out}
    \resumeItemListEnd
  \resumeEntryEnd


\resumeEntryStart
      \resumeEntryTD
      {Data Analysis}{Summer 2020}
    \resumeItemListStart
      \resumeItem {Learned about predictive modelling and basics of machine learning.}
      \resumeItem {Applied predictive modelling and statistical methods to analyse  data of an Insurance company and finding out the probability of failure of payment based on past records.}
      \resumeItem {Learned about predictive modelling and basics of machine learning.}
    \resumeItemListEnd
  \resumeEntryEnd


\resumeEntryStart
      \resumeEntryTD
      {Heat Exchanger}{Autumn 2019}
    \resumeItemListStart
      \resumeItem {Developed a working model of variable temperature outlet heat exchanger from scratch.}
      \resumeItem {The model was awarded 1st prize in TSEC under IICHE (Indian Institute of Chemical Engineers).}
      \resumeItem {The project received praises for it's temperature adjustability and simple scalability.}
    \resumeItemListEnd
  \resumeEntryEnd


\resumeEntryStart
      \resumeEntryTD
      {Steam Trap Health Monitor}{Winter 2017}
    \resumeItemListStart
      \resumeItem {Developed a Steam Trap Health Monitor which works by classifying vibration patterns.}
      \resumeItem {Lead the team of six throughout the whole development operation.}
      \resumeItem {The model reached the semi finals in Smart India Hackathon 2019 (Hardware Edition).}
    \resumeItemListEnd
  \resumeEntryEnd


\resumeEntryStart
      \resumeEntryTD
      {Smart Bin}{Spring 2018}
    \resumeItemListStart
      \resumeItem {Implemented a SMART bin on Arduino UNO microcontroller platform.}
      \resumeItem {Used ultrasonic sensor interfaces to give automatic functioning and moving abilities.}
      \resumeItem {Added support for automated notifications about bin status through use of a GSM module.}
    \resumeItemListEnd
  \resumeEntryEnd

  

\section{\faFlag}{Achievements / Activities}
\resumeEntryStart
  \resumeItem {Qualified for Eyantra 2018 stage 2 held by CSE department of IITB among 200 participating colleges}
  \vspace{-4pt}

  \resumeItem {Presented a poster on treatment of “Recycling of non-recyclable plastics” at Thadomal sahani college for Techfest held under IICHE (Indian Institute of Chemical Engineers)}
  \vspace{-4pt}

  \resumeItem {Presented a review paper design of  horizontal distillation column at ICT Mumbai for OYCE Competition. }
  \vspace{-4pt}

  \resumeItem {Attended an industry-academy programme at DAE Convention BARC (Bhabha Atomic Research Centre).}
  \vspace{-4pt}

  \resumeItem {Ranked 1st in stage 1 of Chemophilia organized by Azeotropy, IIT Bombay}
  \vspace{-4pt}

  \resumeItem {Awarded 1st prize for poster presentation on Science day.}
  \vspace{-4pt}

  \resumeItem {Participated in essay, quiz and debate competition held by office of Deputy Commissioner of central GST}
  \vspace{-4pt}

  \resumeItem {Team Leader in IICDC (Indian Innovation Challenge Design Contest) for development of SMART Helmet.}
  \vspace{-4pt}
 
  \resumeEntryEnd
  
  
\section{\faPieChart}{Positions of Responsibility}
  \vspace{3pt}
 
  \resumeEntryStart
      \resumeEntryTD
      {Department Co. Technical Head}{Sept 2019 - Present}
    \resumeItemListStart
      \resumeItem {Managed social media strategy, branding and street teams to ensure event attendance}
      \resumeItem {Preparing event reports and guiding all event managers regarding event organization}
    \resumeItemListEnd
  \resumeEntryEnd


  
\section{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Technical} {MS-office, AutoCAD, Scilib, Basic Python, DWSIM}
  \vspace{4pt}
  \resumeEntryS{Soft}{Leadership, Communication Skills, Decision making, Social Skills, Time Management}
  \vspace{4pt}
  \resumeEntryS{Hobbies} {Playing Piano, Listening Music, Online surfing, Shopping, Trekking}
  \vspace{4pt}
  \resumeEntryS{Talents} {Stand-up comedy, Negotiation, Event anchoring}
 \resumeEntryEnd

\end{document}
